---
title: "data_analysis_3_bibliometrix"
author: "Sebastian Robledo"
date: "9/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Bibliometric analysis according to these links:*

[*https://www.bibliometrix.org/vignettes/Introduction_to_bibliometrix.html*](https://www.bibliometrix.org/vignettes/Introduction_to_bibliometrix.html){.uri}

[*https://bibliometrix.org/documents/bibliometrix_Report.html*](https://bibliometrix.org/documents/bibliometrix_Report.html){.uri}

# *Getting tidied data*

```{r message=FALSE, warning=FALSE}
data_tidied <- 
  read_csv(here("output",
                "mendelely_tags_wos_scopus.csv"))

data_tidied_wos <- 
  data_tidied |>
  select(SR, CR) |> 
  separate_rows(CR, sep = "; ") |> # Scopus
  count(SR) |>
  filter(n == 1) |> 
  select(SR) |> 
  mutate(database = "wos")

data_tidied <- 
  data_tidied |> 
  left_join(data_tidied_wos) |> 
  mutate(database = if_else(is.na(database), 
                            "Scopus", 
                            database))

```

# *Bibliometrix analysis*

```{r}
results <- biblioAnalysis(data_tidied, sep = ";")
```

```{r}
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
```

```{r}
plot(x = results, k = 10, pause = FALSE)
```

# *Analysis of Cited references*

```{r}
CR <- citations(data_tidied, field = "article", sep = ";")
cbind(CR$Cited[1:10])
```

*The most frequent cited author*

```{r}
CR <- citations(data_tidied, field = "author", sep = ";")
cbind(CR$Cited[1:10])
```

*It is not working...*

*The most frequent local cited authors*

```{r}
CR <- localCitations(data_tidied |> 
                       rename("TI" = title), 
                     sep = ";")
CR$Authors[1:10,]
```

```{r}
CR$Papers[1:10,]
```

# *Authors' Dominance Ranking*

```{r}
DF <- dominance(results, k = 10)
DF
```

# *Authors' h-index*

```{r}
indices <- Hindex(M, field = "author", elements="MARTINEZ-SAEZ N", sep = ";", years = 10)
indices$H
```

# *Top-Authors' productivity over the Time*

```{r}
topAU <- authorProdOverTime(data_tidied, k = 10, graph = TRUE)
```

```{r}
M <- data_tidied |> 
  rename("TI" = title)
k <- 10
M$TC <- as.numeric(M$TC)
data_tidied$PY <- as.numeric(data_tidied$PY)
data_tidied <- data_tidied[!is.na(data_tidied$PY), ]
AU <- names(tableTag(M, "AU"))
k <- min(k, length(AU))
AU <- AU[1:k]
df <- data.frame(Author = "NA", year = NA, TI = "NA", SO = "NA", 
                 DOI = "NA", TC = NA, TCpY = NA, stringsAsFactors = FALSE)
Y <- as.numeric(substr(Sys.time(), 1, 4))
if (!("DI" %in% names(M))) {
  M$DI = "NA"
}
for (i in 1:length(AU)) {
  ind <- which(regexpr(AU[i], M$AU) > -1)
  TCpY <- M$TC[ind]/(Y - M$PY[ind] + 1)
  dfAU <- data.frame(Author = rep(AU[i], length(ind)), 
                     year = M$PY[ind], TI = M$TI[ind], SO = M$SO[ind], 
                     DOI = M$DI[ind], TC = M$TC[ind], TCpY = TCpY, stringsAsFactors = TRUE)
  df <- rbind(df, dfAU)
}
df <- df[-1, ]
df2 <- dplyr::group_by(df, .data$Author, .data$year) %>% 
  dplyr::summarise(freq = length(.data$year), TC = sum(.data$TC), 
                   TCpY = sum(.data$TCpY))
df2 <- as.data.frame(df2)
df2$Author <- factor(df2$Author, levels = AU[1:k])
x <- c(0.5, 1.5 * k/10)
y <- c(min(df$year), min(df$year) + diff(range(df2$year)) * 
         0.125)

```

```{r}
g <- ggplot(df2, aes(x = Author, 
                     y = year, 
                     text = paste("Author: ",
                                  Author, "\nYear: ",
                                  year, "\nN. of Articles: ",
                                  freq, "\nTotal Citations per Year: ",
                                  round(TCpY,
                                        2)
                                  )
                     )
            ) + 
  geom_point(aes(alpha = TCpY, 
                 size = freq), 
             color = "dodgerblue4") + 
  scale_size(range = c(2, 6)) + 
  scale_alpha(range = c(0.3, 1)) + 
  scale_y_continuous(breaks = seq(min(df2$year), 
                                  max(df2$year), 
                                  by = 2)) + 
  guides(size = guide_legend(order = 1,
                             "N.Articles"), 
         alpha = guide_legend(order = 2, 
                              "TC per Year")) + 
  theme(legend.position = "right", text = element_text(color = "#444444"), 
        panel.background = element_rect(fill = "gray97"), 
        panel.grid.minor = element_line(color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#FFFFFF"), 
        plot.title = element_text(size = 24), 
        axis.title = element_text(size = 14, 
                                  color = "#555555"), 
        axis.title.y = element_text(vjust = 1,
                                    angle = 90, 
                                    face = "bold"), 
        axis.title.x = element_text(hjust = 0.95,
                                    face = "bold"), 
        axis.text.x = element_text(face = "bold", 
                                   angle = 90), 
        axis.text.y = element_text(face = "bold")) + 
  labs(title = "Top-Authors' Production over the Time", 
       x = "Author", y = "Year") + 
  geom_line(data = df2, 
            aes(x = Author, y = year, group = Author),
            size = 1, color = "firebrick", alpha = 0.3) + 
  scale_x_discrete(limits = rev(levels(df2$Author))) + 
  coord_flip()
```

```{r}
g
```

# *Keyword co-occurrences* 

```{r}
byproduct_keyword_co_occurrence <- 
  biblioNetwork(data.frame(data_tidied), 
                           analysis = "co-occurrences", 
                           network = "keywords", 
                           sep = ";")

# Plot the network
net=networkPlot(byproduct_keyword_co_occurrence, 
                normalize="association", 
                weighted=T, 
                n = 60, 
                Title = "Keyword Co-occurrences", 
                type = "fruchterman", 
                size=T,
                # dgesize = 5,
                labelsize=0.7)
```

```{r}
dummy_NetMatrix <- biblioNetwork(data.frame(data_tidied |> slice(1:4)), 
                           analysis = "co-occurrences", 
                           network = "keywords", 
                           sep = ";")

# Plot the network
net=networkPlot(dummy_NetMatrix, 
                normalize="association", 
                weighted=T, 
                n = 30, 
                Title = "Keyword Co-occurrences", 
                type = "fruchterman", 
                size=T,
                # dgesize = 5,
                labelsize=0.7)
```

# *Co-Word Analysis: The conceptual structure of a field*

```{r}
CS <- conceptualStructure(data.frame(data_tidied),
                          field="ID", 
                          method="CA", 
                          minDegree=4, 
                          clust=5, 
                          stemming=FALSE, 
                          labelsize=10, 
                          documents=10)
```

# *Historical direct citation network*

```{r}
options(width=130)
histResults <- histNetwork(data.frame(data_tidied) |> 
                             rename("TI" = title), min.citations = 1, sep = ";")

```

```{r}
net <- histPlot(histResults, n=15, size = 10, labelsize=5)
```

[*https://bibliometrix.org/documents/bibliometrix_Report.html*](https://bibliometrix.org/documents/bibliometrix_Report.html)

# *Edu Collaboration Network*

```{r}
NetMatrix <- biblioNetwork(data.frame(data_tidied), analysis = "collaboration",  network = "universities", sep = ";")
net=networkPlot(NetMatrix,  n = 50, Title = "Edu collaboration",type = "auto", size=10,size.cex=T,edgesize = 3,labelsize=0.6)
```
